Specific Gene or Metabolite Levels

### 2025-01-30 Shortcuts_OmicsQuickPlotFunctions.Rmd
gbbKO
serpe data
functions update
updated gene plot functions
fixed level issue in plot.G85R function
improved functions
another tweak
update

---
title: "Specifgic Gene or Metabolite Levels"
author: "John Santiago"
date: "2024-05-24"
output: html_document
---

@@

ID = "ETHR"

@@

@@

gene.name = 'CCAP'

plot.SC(gene.name)

@@

##ID = "0000018"

>>>>

---
title: "Specific Gene or Metabolite Levels"
author: "John Santiago"
date: "2024-05-24"
output: html_document
---

@@

ID = "gbb"

@@

```{r echo = F, fig.width= 10, fig.height=16}

@@

gene.name = "gbb"

plot.serpe.allclusters(gene.name)

```{r echo = F, fig.width=16, fig.height=10}

## Plot expression of a gene set from Single Cell RNAseq experiment
## gene name needs to be the full or partial gene symbol as listed in the table (case sensitive)

heat.genes = c("dpp", "gbb", "put", "wit", "mav", "sax", "tkv", "repo", "ACC", "Ack-like")

serpe.heatmap(heat.genes)

@@
